---
title: "Interactive Data Visualizations"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---
<style type="text/css">
.navbar {
  background-color:#1db954;
}
.main-container {
  max-width: 1600px;
  font-size: 16px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r doc-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import-libraries, include = FALSE}
library(tidyverse)
library(data.table)
library(dplyr)
library(knitr)
library(kableExtra)
library(plotly)
library(widgetframe)
library(RColorBrewer)
```

```{r import-data, echo = FALSE, message = FALSE}
spotify_data <- read_csv("https://raw.githubusercontent.com/hotz1/Spotify-Charts-Project/main/data/spotify_data_full.csv", 
                         col_select = -c(`...1`))
happiness_index <- read_csv("https://raw.githubusercontent.com/hotz1/Spotify-Charts-Project/main/data/happiness_data.csv")
```

```{r merge-data, echo = FALSE}
happiness_small <- happiness_index %>%
  dplyr::select(Country = `Country name`, Region = `Regional indicator`, Happiness = `Ladder score`,
                Lower_CI = lowerwhisker, Upper_CI = upperwhisker, log_GDP_per_capita = `Logged GDP per capita`)

happiness_small[happiness_small == "Hong Kong S.A.R. of China"] <- "Hong Kong"
happiness_small[happiness_small == "Taiwan Province of China"] <- "Taiwan"

spotify_happiness_data <- merge(spotify_data, happiness_small, by = c("Country"))
```

```{r averages-by-country, echo = FALSE}
spotify_avgs_by_country <- spotify_happiness_data %>%
  select(Country, Region, Happiness, Lower_CI, Upper_CI, Danceability,
         Energy, Valence, Weekly_Streams, log_GDP_per_capita) %>%
  group_by(Country) %>%
  mutate(Total_Streams = sum(Weekly_Streams),
         Mean_Danceability = mean(Danceability, na.rm = TRUE),
         Mean_Energy = mean(Energy, na.rm = TRUE),
         Mean_Valence = mean(Valence, na.rm = TRUE),
         Weighted_Mean_Danceability = weighted.mean(Danceability, Weekly_Streams, na.rm = TRUE),
         Weighted_Mean_Energy = weighted.mean(Energy, Weekly_Streams, na.rm = TRUE),
         Weighted_Mean_Valence = weighted.mean(Valence, Weekly_Streams, na.rm = TRUE)) %>%
  select(-c("Danceability", "Energy", "Valence", "Weekly_Streams")) %>%
  ungroup()

spotify_avgs_by_country <- unique(spotify_avgs_by_country)
```

## Highly-Played Track Averages by Country: {.tabset}

The following three plots show the average danceability, energy, and valence of tracks on the Top 200 Spotify Tracks for their respective countries during the first three months of 2022.

In each of the three plots shown below, each country with data on the Spotify Charts website is represented by a circular marker. The marker's size is proportional to the logarithm of the total number of streams among the country's Top 200 Tracks on Spotify during the first three months of 2022, and the marker's colour is chosen based on the region which the country is located in.

### Track Danceability by Country

```{r mean-danceability-by-country, echo = FALSE, fig.width = 10, fig.height = 7}
my_plot <- spotify_avgs_by_country %>%
  plot_ly(type = 'scatter',
          mode = 'markers',
          x = ~Happiness, 
          y = ~Mean_Danceability,
          marker = list(size = ~3*log(Total_Streams/1e6), opacity = 0.9),
          color = ~Region, 
          colors = "Set3",
          text = ~paste("<b>", Country, "</b><br><br>Happiness: ", round(Happiness, 4),
                        "<br>Average Track Danceability: ", round(Mean_Danceability, 4),
                        "<br>Total Streams (millions): ", round(Total_Streams/1e6, 3)),
          hoverinfo = "text")

my_plot <- my_plot %>%
  layout(title = "Mean Track Danceability per Country",
         xaxis = list(title = "Country Happiness"),
         yaxis = list(title = "Track Danceability"))

my_plot
```

### Track Energy by Country

```{r mean-energy-by-country, echo = FALSE, fig.width = 10, fig.height = 7}
my_plot <- spotify_avgs_by_country %>%
  plot_ly(type = 'scatter',
          mode = 'markers',
          x = ~Happiness, 
          y = ~Mean_Energy,
          marker = list(size = ~3*log(Total_Streams/1e6), opacity = 0.9),
          color = ~Region, 
          colors = "Set3",
          text = ~paste("<b>", Country, "</b><br><br>Happiness: ", round(Happiness, 4),
                        "<br>Average Track Energy: ", round(Mean_Energy, 4),
                        "<br>Total Streams (millions): ", round(Total_Streams/1e6, 3)),
          hoverinfo = "text")

my_plot <- my_plot %>%
  layout(title = "Mean Track Energy per Country",
         xaxis = list(title = "Country Happiness"),
         yaxis = list(title = "Track Energy"))

my_plot
```

### Track Valence by Country

```{r mean-valence-by-country, echo = FALSE, fig.width = 10, fig.height = 7}
my_plot <- spotify_avgs_by_country %>%
  plot_ly(type = 'scatter',
          mode = 'markers',
          x = ~Happiness, 
          y = ~Mean_Valence,
          marker = list(size = ~3*log(Total_Streams/1e6), opacity = 0.9),
          color = ~Region, 
          colors = "Set3",
          text = ~paste("<b>", Country, "</b><br><br>Happiness: ", round(Happiness, 4),
                        "<br>Average Track Valence: ", round(Mean_Valence, 4),
                        "<br>Total Streams (millions): ", round(Total_Streams/1e6, 3)),
          hoverinfo = "text")

my_plot <- my_plot %>%
  layout(title = "Mean Track Valence per Country",
         xaxis = list(title = "Country Happiness"),
         yaxis = list(title = "Track Valence"))

my_plot
```

## Averages Weighted by Number of Streams: {.tabset}

Similar to the three plots shown above, the following three plots also show the average danceability, energy, and valence of tracks on the Top 200 Spotify Tracks for their respective countries during the first three months of 2022. As with the plots above, the markers' sizes are proportional to the total number of streams in the country, and the colour of the country's marker is representative of its geopolitical region, as defined by the World Happiness Index data.

However, in this plot, we computed a weighted average of these three metrics, where these metrics are weighted proportionally according to the number of times that the track was streamed in the given country. This may provide a more robust metric than simply computing the means, as weighted means allow us to account for how popular a song is in a particular country.

### Track Danceability by Country

```{r weighted-mean-danceability-by-country, echo = FALSE, fig.width = 10, fig.height = 7}
my_plot <- spotify_avgs_by_country %>%
  plot_ly(type = 'scatter',
          mode = 'markers',
          x = ~Happiness, 
          y = ~Weighted_Mean_Danceability,
          marker = list(size = ~3*log(Total_Streams/1e6), opacity = 0.9),
          color = ~Region, 
          colors = "Set3",
          text = ~paste("<b>", Country, "</b><br><br>Happiness: ", round(Happiness, 4),
                        "<br>Average Track Danceability: ", round(Weighted_Mean_Danceability, 4),
                        "<br>Total Streams (millions): ", round(Total_Streams/1e6, 3)),
          hoverinfo = "text")

my_plot <- my_plot %>%
  layout(title = "Average Track Danceability per Country, Weighted by Number of Streams",
         xaxis = list(title = "Country Happiness"),
         yaxis = list(title = "Track Danceability"))

my_plot
```

### Track Energy by Country

```{r weighted-mean-energy-by-country, echo = FALSE, fig.width = 10, fig.height = 7}
my_plot <- spotify_avgs_by_country %>%
  plot_ly(type = 'scatter',
          mode = 'markers',
          x = ~Happiness, 
          y = ~Weighted_Mean_Energy,
          marker = list(size = ~3*log(Total_Streams/1e6), opacity = 0.9),
          color = ~Region, 
          colors = "Set3",
          text = ~paste("<b>", Country, "</b><br><br>Happiness: ", round(Happiness, 4),
                        "<br>Average Track Energy: ", round(Weighted_Mean_Energy, 4),
                        "<br>Total Streams (millions): ", round(Total_Streams/1e6, 3)),
          hoverinfo = "text")

my_plot <- my_plot %>%
  layout(title = "Average Track Energy per Country, Weighted by Number of Streams",
         xaxis = list(title = "Country Happiness"),
         yaxis = list(title = "Track Energy"))

my_plot
```

### Track Valence by Country

```{r weighted-mean-valence-by-country, echo = FALSE, fig.width = 10, fig.height = 7}
my_plot <- spotify_avgs_by_country %>%
  plot_ly(type = 'scatter',
          mode = 'markers',
          x = ~Happiness, 
          y = ~Weighted_Mean_Valence,
          marker = list(size = ~3*log(Total_Streams/1e6), opacity = 0.9),
          color = ~Region, 
          colors = "Set3",
          text = ~paste("<b>", Country, "</b><br><br>Happiness: ", round(Happiness, 4),
                        "<br>Average Track Valence: ", round(Weighted_Mean_Valence, 4),
                        "<br>Total Streams (millions): ", round(Total_Streams/1e6, 3)),
          hoverinfo = "text")

my_plot <- my_plot %>%
  layout(title = "Average Track Valence per Country, Weighted by Number of Streams",
         xaxis = list(title = "Country Happiness"),
         yaxis = list(title = "Track Valence"))

my_plot
```